Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-07-22 main.tex
:package: Remove unused packages

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{algorithmicx}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage{bookmark}
\usepackage{circuitikz}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{fixmath}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgffor}
\usepackage{pgfgantt}
\usepackage{pgfplots}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage[acronym]{glossaries-extra}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage[short]{optidef}
\usepackage[subtle]{savetrees}

\usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}

\listfiles
\interdisplaylinepenalty=2500
\pgfplotsset{compat=newest}
\usepgfplotslibrary{patchplots,groupplots}
\usetikzlibrary{decorations.pathreplacing,calligraphy}
\usetikzlibrary{arrows,calc,matrix,plotmarks,patterns,positioning}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\DeclareSIUnit{\belm}{Bm}
\DeclareSIUnit{\dBm}{\deci\belm}
\DeclareSIUnit{\beli}{Bi}
\DeclareSIUnit{\dBi}{\deci\beli}
\ctikzset{american}
\usetikzlibrary{arrows,calc,matrix,patterns,pgfplots.groupplots,plotmarks,positioning}

\DeclarePairedDelimiterX{\infdivx}[2]{(}{)}{%
	#1\;\delimsize\|\;#2%
}
\newcommand{\infdiv}{D\infdivx}
\renewcommand{\qedsymbol}{\hfill\ensuremath{\Box}}

\makeatletter
\renewcommand{\fnum@algorithm}{\fname@algorithm{} \thealgorithm:}
\tikzset{
	block/.style={draw,rectangle,align=center},
    from/.style args={#1 to #2}{
        above right={0cm of #1},
        /utils/exec=\pgfpointdiff
            {\tikz@scan@one@point\pgfutil@firstofone(#1)\relax}
            {\tikz@scan@one@point\pgfutil@firstofone(#2)\relax},
        minimum width/.expanded=\the\pgf@x,
        minimum height/.expanded=\the\pgf@y
	}
}
\makeatother

\algrenewcommand{\algorithmicwhile}{\textbf{While}}
\algrenewcommand{\algorithmicif}{\textbf{If}}
\algrenewcommand{\algorithmicthen}{\textbf{Then}}
\algrenewcommand{\algorithmicelse}{\textbf{Else}}
\algrenewcommand{\algorithmicend}{\textbf{End}}
\algrenewcommand{\algorithmicrepeat}{\textbf{Repeat}}
\algrenewcommand{\algorithmicuntil}{\textbf{Until}}
\algrenewcommand{\algorithmicdo}{}

% \algrenewcommand\algorithmicdo{}
% \renewcommand\algorithmicdo{}

\algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
\algrenewcommand{\algorithmicensure}{\textbf{Output:}}

\setabbreviationstyle[acronym]{long-short}

\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dtmac}{DTMAC}{Discrete Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{irs}{IRS}{Intelligent Reflecting Surface}
\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{pin}{PIN}{Positive Intrinsic-Negative}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{tg}{TG}{tag}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}

@@

	A suboptimal \gls{bcd} algorithm is proposed, where the \gls{kkt} input distribution is evaluated in closed form, the active beamforming is updated by \gls{pgd}, and the suboptimal convex decision regions are refined by \gls{dp}.

@@

	\emph{Third,} we evaluate the achievable primary-(total-)backscatter rate region by optimizing the input distribution at Metascatters, the active beamforming at the \gls{ap}, and the decision regions at the user. Since the original problem is highly non-convex, we consider a suboptimal \gls{bcd} algorithm where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is sequentially updated by \gls{pgd} accelerated by backtracking line search, and the decision regions are first restricted to convex, then refined by \gls{dp} and \gls{smawk} algorithm.

@@

\begin{section}{Backscatter Principles}
	% \begin{figure}[!t]
	% 	\centering
	% 	\subfloat[Block Diagram]{
	% 		\resizebox{0.8\columnwidth}{!}{
	% 			\input{assets/block_diagram.tex}
	% 		}
	% 		\label{fi:block_diagram}
	% 	}
	% 	\\
	% 	\subfloat[Equivalent Circuit]{
	% 		\resizebox{0.95\columnwidth}{!}{
	% 			\input{assets/equivalent_circuit.tex}
	% 		}
	% 		\label{fi:equivalent_circuit}
	% 	}
	% 	\\
	% 	\subfloat[Scatter Model]{
	% 		\resizebox{0.8\columnwidth}{!}{
	% 			\input{assets/scatter_model.tex}
	% 		}
	% 		\label{fi:scatter_model}
	% 	}
	% 	\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	% \end{figure}

	\begin{figure*}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.32\linewidth}{!}{
				\input{assets/block_diagram.tex}
			}
			\label{fi:block_diagram}
		}
		\subfloat[Equivalent Circuit]{
			\resizebox{0.37\linewidth}{!}{
				\input{assets/equivalent_circuit.tex}
			}
			\label{fi:equivalent_circuit}
		}
		\subfloat[Scatter Model]{
			\resizebox{0.28\linewidth}{!}{
				\input{assets/scatter_model.tex}
			}
			\label{fi:scatter_model}
		}
		\caption{Block diagram, equivalent circuit, and scatter model of a passive backscatter node. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	\end{figure*}

@@

			\subfloat[Reflection State Distribution]{

@@

					\input{assets/reflection_state_distribution.tex}

@@

			\subfloat[Time Slot Structure]{

@@

					\input{assets/time_block_structure.tex}

@@

				Reflection state distribution and time block structure of \gls{sr}, \gls{irs}, and Metascatter.

@@

\begin{section}{Metascatter-Enabled Network}
	\begin{subsection}{System Model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.8\columnwidth}
			\footnotesize{
				\import{assets/}{metascatter_network.eps_tex}
			}
			\caption{A Metascatter-enabled single-user multi-node network.}
			\label{fi:metascatter_network}
		\end{figure}
		% As shown in Fig. \ref{fi:metascatter_network}, we propose a Metascatter-enabled single-user multi-node network where the spectrum, energy and infrastructures are shared by two coexisting systems.
		As shown in Fig. \ref{fi:metascatter_network}, we propose a Metascatter-enabled single-user multi-node network where two coexisting systems share spectrum, energy and infrastructures.
		% In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
		% In the primary point-to-point system, a $Q$-antenna \gls{ap} transmit to a single-antenna user while assisted by $K$ nearby single-antenna Metascatters.
		The primary point-to-point transmission from a $Q$-antenna \gls{ap} to a single-antenna user is assisted by $K$ nearby single-antenna Metascatters.
		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, $K$ nearby single-antenna Metascatters modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
		For simplicity, we consider a quasi-static block fading model where channels remain constant within coherence interval while vary independently between consecutive blocks.
		% Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol period is $N \in \mathbb{Z}_{++}$ times the primary symbol period.
		Due to physical constraints on load switching, we assume the backscatter symbol period is $N \gg 1$ times longer than primary and consider integer $N$ without loss of generality.
		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.%
		\footnote{
			Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
			One possibility is the \gls{ap} sends training pilots, the tags respond in predefined manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.
		}
		Besides, we omit the signal reflected by two or more times\cite{Wu2019} and ignore the time difference of arrival from different paths\cite{Guo2019b}.

@@

				\input{assets/energy_distribution.tex}

@@

			P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|\mathcal{H}_{m_{\mathcal{K}}}) \dd z,

@@

	\begin{subsection}{Input Distribution}
		% For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent \gls{dtmac} can be formulated by \eqref{eq:dtmac} and problem \eqref{op:weighted_sum_rate} boils down to
		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can construct the equivalent \gls{dtmac} by \eqref{eq:dtmac} and simplify \eqref{op:weighted_sum_rate} to
		\begin{maxi!}
			{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}}}{I(x_{\mathcal{K}})}{\label{op:input_probability_distribution}}{}
			\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
		\end{maxi!}
		which involves coupled term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex when $K > 1$. Next, we propose a numerical method that evaluate the \gls{kkt} input distribution by limit of sequences.
		\begin{remark}
			% As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are only necessary for such kind of problems and these solutions may end up being saddle points.
			As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are generally necessary but insufficient for total rate maximization in discrete memoryless \gls{mac}. Therefore, \gls{kkt} solutions may end up being saddle points of problem \eqref{op:input_probability_distribution}.
		\end{remark}
		Following \cite{Rezaeian2004}, we first recast \gls{kkt} conditions to their equivalent form for problem \eqref{op:input_probability_distribution}, then propose an iterative method that guarantees input distribution satisfying above conditions on convergence.
		% Interestingly, the total-rate optimal input design for general discrete memoryless \gls{mac} remains an open problem, and we instead propose a \gls{kkt} solution to problem \eqref{op:input_probability_distribution}.
		\begin{proposition}
			% The \gls{kkt} optimality conditions for problem \eqref{op:input_probability_distribution} are equivalent to, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$,
			The \gls{kkt} optimality conditions for problem \eqref{op:input_probability_distribution} are equivalent to, $\forall k,m_k$,
			\begin{subequations}
				\label{eq:input_kkt_condition}
				\begin{alignat}{2}
					I_k^\star(x_{m_k}) & = I^\star(x_{\mathcal{K}}), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
					I_k^\star(x_{m_k}) & \le I^\star(x_{\mathcal{K}}), \quad &  & P_k^\star(x_{m_k}) = 0.\label{eq:dropped_states}
				\end{alignat}
			\end{subequations}
			\label{pr:input_kkt_condition}
		\end{proposition}

@@

			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \dd z}{(N-1)!}

@@

@@

						\State Set $\gamma\gets\beta\gamma$

@@

	\begin{subsection}{Decision Threshold}
		% Once node input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and active beamforming vector $\boldsymbol{w}$ are obtained, problem \eqref{op:weighted_sum_rate}
		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{w}$, problem \eqref{op:weighted_sum_rate} reduces to
		\begin{maxi!}
			{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}\in\mathbb{R}_+^{L+1}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
			\addConstraint{\eqref{co:decision_threshold}.}
		\end{maxi!}

		\begin{remark}
			Ideally, backscatter detection (and decision design) has no impact on primary achievable rate.
			When nodes transmit at non-zero total rate, the user can re-encode backscatter messages to recover coded backscatter symbol $x_{\mathcal{K}}$ at each block. Otherwise, $x_{\mathcal{K}}$ can be deterministic and known to the user.
			% Decision threshold only influences backscatter rate instead of primary rate.
		\end{remark}

		\begin{remark}
			% With input distribution of all nodes, we can formulate an equivalent information source with augmented alphabet of tag input combination.
			% In terms of total backscatter rate, we can formulate an equivalent information source with augmented alphabet of tag input combination.
			% When input distribution of all nodes are available, we can formulate an equivalent information source in terms of total backscatter rate.
			% When input distribution of all nodes are available, we can think an equivalent information source with augmented alphabet of state tuple, in terms of total backscatter rate.
			In terms of total backscatter rate, we can regard all nodes as an equivalent information source with augmented alphabet of node state tuple $x_{m_{\mathcal{K}}}$.
			As such, the \gls{dtmac} \eqref{eq:dtmac} is essentially a \gls{dmtc}, and decision threshold design can be simplified accordingly.
		\end{remark}

		Interestingly, the optimal threshold design to maximize the mutual information for a general \gls{dmtc} with a fixed number of output letters remains an open issue.
		The reason is that each decision region may contain more than one disjoint partitions (i.e., non-convex) and the number of thresholds are unknown.
		Fortunately, for the proposed energy detection, we proved that the \gls{dmtc} capacity can be achieved using only convex decision regions.
		This conclusion is summarized below.

>>>>

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bookmark}
\usepackage[american]{circuitikz}
\usepackage{cite}
\usepackage{fixmath}
\usepackage[acronym]{glossaries-extra}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage[short]{optidef}
\usepackage{pgfplots}
\usepackage[subtle]{savetrees}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tikz}
\usepackage{xcolor}

% \usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}

% amsthm
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}

% siunitx
\DeclareSIUnit{\belm}{Bm}
\DeclareSIUnit{\dBm}{\deci\belm}
\DeclareSIUnit{\beli}{Bi}
\DeclareSIUnit{\dBi}{\deci\beli}

% PGF/TikZ
\usetikzlibrary{arrows,calc,matrix,patterns,plotmarks,positioning}
\usepgfplotslibrary{groupplots,patchplots}
\pgfplotsset{compat=newest}

% algpseudocode
\makeatletter
\renewcommand{\fnum@algorithm}{\fname@algorithm{} \thealgorithm:}
\makeatother
\algrenewcommand{\algorithmicrequire}{\textbf{Input:}}
\algrenewcommand{\algorithmicensure}{\textbf{Output:}}
\algrenewcommand{\algorithmicwhile}{\textbf{While}}
\algrenewcommand{\algorithmicend}{\textbf{End}}
\algrenewcommand{\algorithmicrepeat}{\textbf{Repeat}}
\algrenewcommand{\algorithmicuntil}{\textbf{Until}}
\algrenewcommand{\algorithmicdo}{}

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dtmac}{DTMAC}{Discrete Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{irs}{IRS}{Intelligent Reflecting Surface}
\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}

@@

	% A suboptimal \gls{bcd} algorithm is proposed, where the \gls{kkt} input distribution is numerically evaluated in closed form, the active beamforming is iteratively updated by \gls{pgd}, and the decision regions are restricted to convex and opty
	% We then propose a suboptimal \gls{bcd} algorithm that numerically evaluates the \gls{kkt} input distribution in closed form, iteratively updates the active beamforming by \gls{pgd}, and employs existing thresholding schemes to refine suboptimal convex decision regions.
	A suboptimal \gls{bcd} algorithm is proposed, which numerically evaluates the \gls{kkt} input distribution in closed form, iteratively updates the active beamforming by \gls{pgd}, and employs existing thresholding schemes for suboptimal convex decision regions.

@@

	\emph{Third,} we evaluate the achievable primary-(total-)backscatter rate region by optimizing the input distribution at Metascatters, the active beamforming at the \gls{ap}, and the decision regions at the user. Since the original problem is highly non-convex, we consider a suboptimal \gls{bcd} algorithm where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by backtracking line search, and the decision regions are first restricted to convex, then refined by existing thresholding designs.

@@

\begin{section}{Backscatter Principles}
	% \begin{figure}[!t]
	% 	\centering
	% 	\subfloat[Block Diagram]{
	% 		\resizebox{0.8\columnwidth}{!}{
	% 			\input{assets/illustration/block_diagram.tex}
	% 		}
	% 		\label{fi:block_diagram}
	% 	}
	% 	\\
	% 	\subfloat[Equivalent Circuit]{
	% 		\resizebox{0.95\columnwidth}{!}{
	% 			\input{assets/illustration/equivalent_circuit.tex}
	% 		}
	% 		\label{fi:equivalent_circuit}
	% 	}
	% 	\\
	% 	\subfloat[Scatter Model]{
	% 		\resizebox{0.8\columnwidth}{!}{
	% 			\input{assets/illustration/scatter_model.tex}
	% 		}
	% 		\label{fi:scatter_model}
	% 	}
	% 	\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	% \end{figure}

	\begin{figure*}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.32\linewidth}{!}{
				\input{assets/illustration/block_diagram.tex}
			}
			\label{fi:block_diagram}
		}
		\subfloat[Equivalent Circuit]{
			\resizebox{0.37\linewidth}{!}{
				\input{assets/illustration/equivalent_circuit.tex}
			}
			\label{fi:equivalent_circuit}
		}
		\subfloat[Scatter Model]{
			\resizebox{0.28\linewidth}{!}{
				\input{assets/illustration/scatter_model.tex}
			}
			\label{fi:scatter_model}
		}
		\caption{Block diagram, equivalent circuit, and scatter model of a passive backscatter node. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	\end{figure*}

@@

			\subfloat[Input Distribution]{

@@

					\input{assets/illustration/input_distribution.tex}

@@

			\subfloat[Time Block]{

@@

					\input{assets/illustration/time_block.tex}

@@

				Input probability distribution and time block structure of \gls{sr}, \gls{irs}, and Metascatter.

@@

\begin{section}{Metascatter-Enabled Network}
	\begin{subsection}{System Model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.8\columnwidth}
			\footnotesize{
				\import{assets/illustration/}{metascatter_network.eps_tex}
			}
			\caption{A Metascatter-enabled single-user multi-node network.}
			\label{fi:metascatter_network}
		\end{figure}
		% As shown in Fig. \ref{fi:metascatter_network}, we propose a Metascatter-enabled single-user multi-node network where the spectrum, energy and infrastructures are shared by two coexisting systems.
		As shown in Fig. \ref{fi:metascatter_network}, we propose a Metascatter-enabled single-user multi-node network where two coexisting systems share spectrum, energy and infrastructures.
		% In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
		% In the primary point-to-point system, a $Q$-antenna \gls{ap} transmit to a single-antenna user while assisted by $K$ nearby single-antenna Metascatters.
		The primary point-to-point transmission from a $Q$-antenna \gls{ap} to a single-antenna user is assisted by $K$ nearby single-antenna Metascatters.
		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, $K$ nearby single-antenna Metascatters modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
		For simplicity, we consider a quasi-static block fading model where channels remain constant within coherence interval while vary independently between consecutive blocks.
		% Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol period is $N \in \mathbb{Z}_{++}$ times the primary symbol period.
		Due to physical constraints on load switching, we assume the backscatter symbol period is $N \gg 1$ times longer than primary and consider integer $N$ without loss of generality.
		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.%
		\footnote{
			Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
			One possibility is the \gls{ap} sends training pilots, the tags respond in predefined manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.
		}
		Besides, we omit the signal reflected by two or more times\cite{Wu2019} and ignore the time difference of arrival from different paths\cite{Guo2019b}.

@@

				\input{assets/illustration/energy_distribution.tex}

@@

			P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|\mathcal{H}_{m_{\mathcal{K}}}) \, d z,

@@

	\begin{subsection}{Input Distribution}
		% For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent \gls{dtmac} can be formulated by \eqref{eq:dtmac} and problem \eqref{op:weighted_sum_rate} boils down to
		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can construct the equivalent \gls{dtmac} by \eqref{eq:dtmac} and simplify \eqref{op:weighted_sum_rate} to
		\begin{maxi!}
			{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}}}{I(x_{\mathcal{K}})}{\label{op:input_distribution}}{}
			\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
		\end{maxi!}
		which involves coupled term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex when $K > 1$. Next, we propose a numerical method that evaluate the \gls{kkt} input distribution by limit of sequences.
		\begin{remark}
			% As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are only necessary for such kind of problems and these solutions may end up being saddle points.
			As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are generally necessary but insufficient for total rate maximization in discrete memoryless \gls{mac}. Therefore, \gls{kkt} solutions may end up being saddle points of problem \eqref{op:input_distribution}.
		\end{remark}
		Following \cite{Rezaeian2004}, we first recast \gls{kkt} conditions to their equivalent form for problem \eqref{op:input_distribution}, then propose an iterative method that guarantees input distribution satisfying above conditions on convergence.
		% Interestingly, the total-rate optimal input design for general discrete memoryless \gls{mac} remains an open problem, and we instead propose a \gls{kkt} solution to problem \eqref{op:input_distribution}.
		\begin{proposition}
			% The \gls{kkt} optimality conditions for problem \eqref{op:input_distribution} are equivalent to, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$,
			The \gls{kkt} optimality conditions for problem \eqref{op:input_distribution} are equivalent to, $\forall k,m_k$,
			\begin{subequations}
				\label{eq:input_kkt_condition}
				\begin{alignat}{2}
					I_k^\star(x_{m_k}) & = I^\star(x_{\mathcal{K}}), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
					I_k^\star(x_{m_k}) & \le I^\star(x_{\mathcal{K}}), \quad &  & P_k^\star(x_{m_k}) = 0.\label{eq:dropped_states}
				\end{alignat}
			\end{subequations}
			\label{pr:input_kkt_condition}
		\end{proposition}

@@

			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!}

@@

					\State \phantom{Update} $\gamma^{(r)}\gets\gamma$

@@

						\State Set $\gamma^{(r)}\gets\beta\gamma^{(r)}$

@@

	\begin{subsection}{Decision Threshold}
		% Once node input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and active beamforming vector $\boldsymbol{w}$ are obtained, problem \eqref{op:weighted_sum_rate}
		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{w}$, problem \eqref{op:weighted_sum_rate} reduces to
		\begin{maxi!}
			{\scriptstyle{\boldsymbol{t}\in\mathbb{R}_+^{L+1}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
			\addConstraint{\eqref{co:decision_threshold},}
		\end{maxi!}
		where it is trivial to conclude $t_0^\star=0$ and $t_L^\star=\infty$ for energy-based backscatter detection.

		\begin{remark}
			Backscatter detection (and decision design) has no impact on primary achievable rate.
			When nodes transmit at non-zero total rate, the user can re-encode backscatter messages to recover coded backscatter tuple $x_{\mathcal{K}}$ at each block.
			Otherwise, $x_{\mathcal{K}}$ can be fully deterministic and known to the user.
			% Once backscatter messages are successfully decoded, the user can re-encode backscatter messages to recover coded backscatter tuple $x_{\mathcal{K}}$ at each block.
			% Upon successful backscatter detection, the user can re-encode backscatter messages to recover coded backscatter tuple $x_{\mathcal{K}}$ at each block.
			% Therefore, decision design has no impact on primary achievable rate.
			% Decision threshold only influences backscatter rate instead of primary rate.
			\label{re:backscatter_detection}
		\end{remark}

		Remark \ref{re:backscatter_detection} suggests any $\boldsymbol{t}$ maximizes total backscatter mutual information $I^{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})$ is also optimal for problem \eqref{op:decision_threshold}.
